Why Donors Donate?

### 2020-09-17 analysis/05_market_simulator.Rmd
testing matrix multiplication to find issue with market shres not lining up with excel sheet. Also made capitalization consistent in inputs

                        "Very little trust in polticial institutions",
                        "Little trust in polticial institutions",
                        "Nuetral trust in polticial institutions",
                        "Some trust in polticial institutions",
                        "A lot of trust in polticial institutions",
                        "Complete trust in polticial institutions",

@@

                        "Donate At least once a month", 

@@

                        "Active sonsumer member",

@@

# beta_persona_test <- as.data.frame(matrix(rep(0), nrow = 38))
# 
# beta_persona_test$levels = c("Persona 1", "Persona 2", "Persona 3", "Chartiy Importance", "Trust in Charity", "Donation Frequency", "Donation Amount", "Volunteer 12 Months", "Volunteer Frequence","Personal Activism", "Family Activism", "Religious Membership", "Sport or Recreational Membership", "Art, Music, or Educational Membership","Labor Union Membership", "Political Party Membership", "Environmental Organization Membership", "Professional Association", "Humanitarian or Charity Membership","Consumer Organization Membership", "Other Organization Membership", "Follow National News", "Follow International News", "News Medium","Follow Government or Public Affairs", "Travel to Developing Countries", "Political Preference", "Trust in Political Institutions", "Others Should be Charitable", "Worship Service Attendence", "Religious Importance", "Religion", "Gender", "Marital Status", "Education", "Income", "Race", "Age")
# 
# 
# 
# # Persona Reactive Element
# 
# beta_persona_test$p1 <- 1
# 
# beta_persona_test$p2 <- 2
# 
# beta_persona_test$p3 <- 3
#         
# persona1 <- persona_data[,2]
# 
# p_beta1 <- as.matrix(public_political_social_charity_demo) %*%   
#   
#   as.matrix(persona1) %*% beta_persona_test[,3]

@@

  # Organization name inputs
  df[,2] <- rep(c(input$ai_id, input$gp_id, input$ox_id, input$rc_id),6)
  # Type of value
  df[,3] <- c(rep("Utility", 4), rep("Market Share", 4))
  # Persona name inputs
  df[,4] <- c(rep(input$p1_id,8), rep(input$p2_id, 8), rep(input$p3_id, 8))

@@

textInput("p1_id",
          label = "Persona Name",
          value = "Persona 1",
          placeholder = "Enter Persona Name")

selectInput("p1_national_news",
         label = "Follow national news:",
         choices = c("Rarely",
                     "Once a week",
                     "At least once a day"),
         selected = "At least once a day")

selectInput("p1_international_news",
         label = "Follow international news:",
         choices = c("Never",
                     "Sometimes",
                     "Always"),
         selected = "Always")

selectInput("p1_news_medium",
         label = "Medium to follow news:",
         choices = c("TV",
                     "Print",
                     "Online (not social media)",
                     "Social media",
                     "Radio",
                     "Email newsletter",
                     "News app"),
         multiple = TRUE,
         selected = c("TV", "Print", "Social media"))

selectInput("p1_follow_gov",
         label = "Follow government & public affairs:",
         choices = c("Not Often",
                     "Often"),
         selected = "Often")

#Fix
selectInput("p1_travel_developing",
         label = "Travel to developing country:",
         choices = c("Doesn't travel", "Does travel"),
         selected = "Does travel")

selectInput("p1_political_pref",
         label = "Political views from liberal to conservative:",
         choices = c("Extremely liberal",
                     "Somewhat liberal",
                     "Slightly liberal",
                     "Moderate",
                     "Slightly conservative",
                     "Somewhat conservative",
                     "Extremely conservative"),
         selected = "Somewhat liberal")

#Fix
selectInput("p1_institution_trust",
         label = "Political institution trust from none to complete:",
         choices = c("No trust at all in political institutions",
                     "Very little trust in political institutions",
                     "Little trust in political institutions",
                     "Nuetral trust in political institutions",
                     "Some trust in political institutions",
                     "A lot of trust in political institutions",
                     "Complete trust in political institutions"),
         selected = "Complete trust in political institutions ")

selectInput("p1_others_charitable",
         label = "People should be more charitable:",
         choices = c("Strongly Disagree",
                     "Disagree",
                     "Somewhat disagree",
                     "Nuetral",
                     "Somewhat agree",
                     "Agree",
                     "Strongly agree"),
         selected = "Strongly agree")

# Fix
selectInput("p1_worship_attendance",
         label = "Worship service attendance:",
         choices = c("Not sure",
                     "Rarely attend services",
                     "Attend at least once a month"),
         selected = "Attend at least once a month")

selectInput("p1_religion_importance",
         label = "Importance of religion:",
         choices = c("Not important",
                     "Important"),
         selected = "Important")

selectInput("p1_religion",
         label = "Religion:",
         choices = c('Catholic',
                     'Protestant',
                     'Christian Orthodox',
                     'Jewish',
                     'Muslim',
                     'Sikh',
                     'Hindu',
                     'Buddhist',
                     'Atheist',
                     'Other (Religion)'),
         selected = 'Protestant')

selectInput("p1_charity_importance",
          label = "Charity Importance:",
          choices = c("Not at all important",
                      "Very unimportant",
                      "Somewhat unimportant",
                      "Nuetral",
                      "Somewhat important",
                      "Very important",
                      "Essential"),
          selected = "Somewhat unimportant")

#Fix
selectInput("p1_trust_in_charity",
            label = "Charity Trust:",
            choices = c("No trust at all in charities",
                        "Very little trust in charities",
                        "Little trust in charities",
                        "Nuetral trust in charities",
                        "Some trust in charities",
                        "A lot of trust in charities",
                        "Complete trust in charities"),
            selected = "Complete trust in charities")

#Fix
selectInput("p1_donation_frequency",
         label = "Donation Frequency:",
         choices = c('Donate more than once a month, less than once a year',
                     'Donate at least once a month'),
         selected = "Donate at least once a month")

selectInput("p1_donation_amount",
         label = "Donation Amount:",
         choices = c("$1-$49",
                     '$50-$99',
                     '$100-$499',
                     '$500-$999',
                     '$1,000-$4,999',
                     '$5,000-$9,999',
                     '$10,000+'),
         selected = "$100-$499")

#Fix
selectInput("p1_volunteer_12",
         label = "Volunteered in last 12 Months:",
         choices = c("Haven't volunteered", "Have volunteered"),
         selected = "Have volunteered")

#Fix
selectInput("p1_volunteer_frequency",
         label = "Volunteer Frequency:",
         choices = c("Haven't volunteered in past 12 months",
                     "Rarely volunteer",
                     "Volunteer more than once a month, less than once a year",
                     "Volunteer at least once a month"),
         selected = "Volunteer at least once a month")

# fix
selectInput("p1_personal_activism",
         label = "Personal Activism:",
         choices = c('Not personally involved ',
                     'Personally involved'),
         selected = "Personally involved")

#Fix
selectInput("p1_family_activism",
         label = "Family Activism:",
         choices = c('Family not involved',
                     'Family involved'),
         selected = "Family involved")

#Fix
selectInput("p1_religious_member",
         label = "Church Membership:",
         choices = c("Don't belong to church membership",
                     'Inactive church member',
                     'Active church member'),
         selected = "Don't belong to church membership")

#Fix
selectInput("p1_sport_member",
         label = "Sport or Recreational Membership:",
         choices = c("Don't belong to sports membership",
                     'Inactive sports member',
                     'Active sports member'),
         selected = "Don't belong to sports membership")
#Fix
selectInput("p1_art_member",
         label = "Art, Music, or Educational Membership:",
         choices = c("Don't belong to educational membership",
                     'Inactive educational member',
                     'Active educational member'),
         selected = "Don't belong to educational membership")
#Fix
selectInput("p1_labor_member",
         label = "Labor Union Membership:",
         choices = c("Don't belong to union",
                     'Inactive union member',
                     'Active union member'),
         selected = "Don't belong to union")

#Fix
selectInput("p1_political_member",
         label = "Political Party Membership:",
         choices = c("Don't belong to party",
                     'Inactive party member',
                     'Active party member'),
         selected = "Active party member")
# Fix
selectInput("p1_environmental_member",
         label = "Environmental Org. Membership:",
         choices = c("Don't belong to environmental organization",
                     'Inactive environmental member',
                     'Active environmental member'),
         selected = "Don't belong to environmental organization")
# Fix
selectInput("p1_professional_member",
         label = "Professional Membership:",
         choices = c("Don't belong to professional membership",
                     'Inactive professional member',
                     'Active professional member'),
         selected = "Don't belong to professional membership")
# Fix
selectInput("p1_humanitarian_member",
         label = "Humanitarian Org. Membership:",
         choices = c("Don't belong to humanitarian organization",
                     'Inactive humanitarian member',
                     'Active humanitarian member'),
         selected = "Active humanitarian member")

# Fix
selectInput("p1_consumer_member",
         label = "Consumer Org. Membership:",
         choices = c("Don't belong to consumer organization",
                     'Inactive consumer member',
                     'Active consumer member'),
         selected = "Don't belong to consumer organization")
# Fix
selectInput("p1_other_member",
         label = "Other Org. Membership:",
         choices = c("Don't belong to other organization",
                     'Inactive other member',
                     'Active other member'),
         selected = "Don't belong to other organization")

selectInput("p1_gender",
         label = "Gender:",
         choices = c("Male",
                     "Female",
                     "Transgender",
                     "Prefer not to say",
                     "Other (Gender)"),
         selected = "Male")

selectInput("p1_marital_status",
         label = "Marital Status:",
         choices = c("Married",
                     "Widowed",
                     "Divorced",
                     "Separated",
                     "Never married"),
         selected = "Married")

selectInput("p1_education",
         label = "Education:",
         choices = c("Less than high school",
                     "High school graduate",
                     "Some college",
                     "2 year degree",
                     "4 year degree",
                     "Graduate or professional degree",
                     "Doctorate"),
         selected = "2 year degree")

selectInput("p1_income",
         label = "Income:",
         choices = c('Less than median of $61,372',
                     'More than median of $61,372'),
         selected = "More than median of $61,372")

selectInput("p1_race",
         label = "Race(s):",
         choices = c('White',
                     'Black or African American',
                     'American Indian or Alaska Native',
                     'Asian',
                     'Native Hawaiian or Pacific Islander',
                     'Other (Race)'),
         multiple = TRUE,
         selected = "White")

selectInput("p1_age",
         label = "Age:",
         choices = c('Less than median age of 36',
                     "More than median age of 36"),
         selected = "Less than median age of 36")

@@

textInput("p2_id",
          label = "Persona Name",
          value = "Persona 2",
          placeholder = "Enter Persona Name")

selectInput("p2_national_news",
         label = "Follow national news:",
         choices = c("Rarely",
                     "Once a week",
                     "At least once a day"),
         selected = "At least once a day")

selectInput("p2_international_news",
         label = "Follow international news:",
         choices = c("Never",
                     "Sometimes",
                     "Always"),
         selected = "Always")

selectInput("p2_news_medium",
         label = "Medium to follow news:",
         choices = c("TV",
                     "Print",
                     "Online (not social media)",
                     "Social media",
                     "Radio",
                     "Email newsletter",
                     "News app"),
         multiple = TRUE,
         selected = c("TV", "Print", "Social media"))

selectInput("p2_follow_gov",
         label = "Follow government & public affairs:",
         choices = c("Not Often",
                     "Often"),
         selected = "Often")

#Fix
selectInput("p2_travel_developing",
         label = "Travel to developing country:",
         choices = c("Doesn't travel", "Does travel"),
         selected = "Does travel")

selectInput("p2_political_pref",
         label = "Political views from liberal to conservative:",
         choices = c("Extremely liberal",
                     "Somewhat liberal",
                     "Slightly liberal",
                     "Moderate",
                     "Slightly conservative",
                     "Somewhat conservative",
                     "Extremely conservative"),
         selected = "Somewhat liberal")

#Fix
selectInput("p2_institution_trust",
         label = "Political institution trust from none to complete:",
         choices = c("No trust at all in political institutions",
                     "Very little trust in political institutions",
                     "Little trust in political institutions",
                     "Nuetral trust in political institutions",
                     "Some trust in political institutions",
                     "A lot of trust in political institutions",
                     "Complete trust in political institutions"),
         selected = "Complete trust in political institutions ")

selectInput("p2_others_charitable",
         label = "People should be more charitable:",
         choices = c("Strongly Disagree",
                     "Disagree",
                     "Somewhat disagree",
                     "Nuetral",
                     "Somewhat agree",
                     "Agree",
                     "Strongly agree"),
         selected = "Strongly agree")

# Fix
selectInput("p2_worship_attendance",
         label = "Worship service attendance:",
         choices = c("Not sure",
                     "Rarely attend services",
                     "Attend at least once a month"),
         selected = "Attend at least once a month")

selectInput("p2_religion_importance",
         label = "Importance of religion:",
         choices = c("Not important",
                     "Important"),
         selected = "Important")

selectInput("p2_religion",
         label = "Religion:",
         choices = c('Catholic',
                     'Protestant',
                     'Christian Orthodox',
                     'Jewish',
                     'Muslim',
                     'Sikh',
                     'Hindu',
                     'Buddhist',
                     'Atheist',
                     'Other (Religion)'),
         selected = 'Protestant')

selectInput("p2_charity_importance",
          label = "Charity Importance:",
          choices = c("Not at all important",
                      "Very unimportant",
                      "Somewhat unimportant",
                      "Nuetral",
                      "Somewhat important",
                      "Very important",
                      "Essential"),
          selected = "Somewhat unimportant")

#Fix
selectInput("p2_trust_in_charity",
            label = "Charity Trust:",
            choices = c("No trust at all in charities",
                        "Very little trust in charities",
                        "Little trust in charities",
                        "Nuetral trust in charities",
                        "Some trust in charities",
                        "A lot of trust in charities",
                        "Complete trust in charities"),
            selected = "Complete trust in charities")

#Fix
selectInput("p2_donation_frequency",
         label = "Donation Frequency:",
         choices = c('Donate more than once a month, less than once a year',
                     'Donate at least once a month'),
         selected = "Donate at least once a month")

selectInput("p2_donation_amount",
         label = "Donation Amount:",
         choices = c("$1-$49",
                     '$50-$99',
                     '$100-$499',
                     '$500-$999',
                     '$1,000-$4,999',
                     '$5,000-$9,999',
                     '$10,000+'),
         selected = "$100-$499")

#Fix
selectInput("p2_volunteer_12",
         label = "Volunteered in last 12 Months:",
         choices = c("Haven't volunteered", "Have volunteered"),
         selected = "Have volunteered")

#Fix
selectInput("p2_volunteer_frequency",
         label = "Volunteer Frequency:",
         choices = c("Haven't volunteered in past 12 months",
                     "Rarely volunteer",
                     "Volunteer more than once a month, less than once a year",
                     "Volunteer at least once a month"),
         selected = "Volunteer at least once a month")

# fix
selectInput("p2_personal_activism",
         label = "Personal Activism:",
         choices = c('Not personally involved ',
                     'Personally involved'),
         selected = "Personally involved")

#Fix
selectInput("p2_family_activism",
         label = "Family Activism:",
         choices = c('Family not involved',
                     'Family involved'),
         selected = "Family involved")

#Fix
selectInput("p2_religious_member",
         label = "Church Membership:",
         choices = c("Don't belong to church membership",
                     'Inactive church member',
                     'Active church member'),
         selected = "Don't belong to church membership")

#Fix
selectInput("p2_sport_member",
         label = "Sport or Recreational Membership:",
         choices = c("Don't belong to sports membership",
                     'Inactive sports member',
                     'Active sports member'),
         selected = "Don't belong to sports membership")
#Fix
selectInput("p2_art_member",
         label = "Art, Music, or Educational Membership:",
         choices = c("Don't belong to educational membership",
                     'Inactive educational member',
                     'Active educational member'),
         selected = "Don't belong to educational membership")
#Fix
selectInput("p2_labor_member",
         label = "Labor Union Membership:",
         choices = c("Don't belong to union",
                     'Inactive union member',
                     'Active union member'),
         selected = "Don't belong to union")

#Fix
selectInput("p2_political_member",
         label = "Political Party Membership:",
         choices = c("Don't belong to party",
                     'Inactive party member',
                     'Active party member'),
         selected = "Active party member")
# Fix
selectInput("p2_environmental_member",
         label = "Environmental Org. Membership:",
         choices = c("Don't belong to environmental organization",
                     'Inactive environmental member',
                     'Active environmental member'),
         selected = "Don't belong to environmental organization")
# Fix
selectInput("p2_professional_member",
         label = "Professional Membership:",
         choices = c("Don't belong to professional membership",
                     'Inactive professional member',
                     'Active professional member'),
         selected = "Don't belong to professional membership")
# Fix
selectInput("p2_humanitarian_member",
         label = "Humanitarian Org. Membership:",
         choices = c("Don't belong to humanitarian organization",
                     'Inactive humanitarian member',
                     'Active humanitarian member'),
         selected = "Active humanitarian member")

# Fix
selectInput("p2_consumer_member",
         label = "Consumer Org. Membership:",
         choices = c("Don't belong to consumer organization",
                     'Inactive consumer member',
                     'Active consumer member'),
         selected = "Don't belong to consumer organization")
# Fix
selectInput("p2_other_member",
         label = "Other Org. Membership:",
         choices = c("Don't belong to other organization",
                     'Inactive other member',
                     'Active other member'),
         selected = "Don't belong to other organization")

selectInput("p2_gender",
         label = "Gender:",
         choices = c("Male",
                     "Female",
                     "Transgender",
                     "Prefer not to say",
                     "Other (Gender)"),
         selected = "Male")

selectInput("p2_marital_status",
         label = "Marital Status:",
         choices = c("Married",
                     "Widowed",
                     "Divorced",
                     "Separated",
                     "Never married"),
         selected = "Married")

selectInput("p2_education",
         label = "Education:",
         choices = c("Less than high school",
                     "High school graduate",
                     "Some college",
                     "2 year degree",
                     "4 year degree",
                     "Graduate or professional degree",
                     "Doctorate"),
         selected = "Some college")

selectInput("p2_income",
         label = "Income:",
         choices = c('Less than median of $61,372',
                     'More than median of $61,372'),
         selected = "More than median of $61,372")

selectInput("p2_race",
         label = "Race(s):",
         choices = c('White',
                     'Black or African American',
                     'American Indian or Alaska Native',
                     'Asian',
                     'Native Hawaiian or Pacific Islander',
                     'Other (Race)'),
         multiple = TRUE,
         selected = "American Indian or Alaska Native")

>>>>

                        "Very little trust in political institutions",
                        "Little trust in political institutions",
                        "Nuetral trust in political institutions",
                        "Some trust in political institutions",
                        "A lot of trust in political institutions",
                        "Complete trust in political institutions",

@@

                        "Donate at least once a month", 

@@

                        "Active consumer member",

@@

test_beta <- as.data.frame(matrix(rep(0), nrow = 12))

test_beta$levels = c("Persona 1", "Persona 2", "Persona 3", "input1", "input2", "input3", "input4", "input5", "input6", "input7", "input8", "input9")

# Persona Reactive Element

test_beta$p1 <- 0
test_beta$p1[1] <- 1

test_beta$p2 <- 0
test_beta$p2[2] <- 1

test_beta$p3 <- 0
test_beta$p3[3] <- 1

test1 <- test_beta[,3]

@@

  # Organization name inputs
  df[,2] <- c(input$ai_id, input$gp_id, input$ox_id, input$rc_id)
  # Type of value
  df[,3] <- c(rep("Utility", 4), rep("Market Share", 4))
  # Persona name inputs
  df[,4] <- c(rep(input$p1_id,8), rep(input$p2_id, 8), rep(input$p3_id, 8))

@@

textInput("p1_id",
          label = "Persona name",
          value = "Persona 1",
          placeholder = "Enter persona name",
          width = "450px")

selectInput("p1_national_news",
         label = "Follow national news:",
         choices = c("Rarely",
                     "Once a week",
                     "At least once a day"),
         selected = "At least once a day",
         width = "450px")

selectInput("p1_international_news",
         label = "Follow international news:",
         choices = c("Never",
                     "Sometimes",
                     "Always"),
         selected = "Always",
         width = "450px")

selectInput("p1_news_medium",
         label = "Medium to follow news:",
         choices = c("TV",
                     "Print",
                     "Online (not social media)",
                     "Social media",
                     "Radio",
                     "Email newsletter",
                     "News app"),
         multiple = TRUE,
         selected = c("TV", "Print", "Social media"),
         width = "450px")

selectInput("p1_follow_gov",
         label = "Follow government & public affairs:",
         choices = c("Not often",
                     "Often"),
         selected = "Often",
         width = "450px")

#Fix
selectInput("p1_travel_developing",
         label = "Travel to developing country:",
         choices = c("Doesn't travel", "Does travel"),
         selected = "Does travel",
         width = "450px")

selectInput("p1_political_pref",
         label = "Political views from liberal to conservative:",
         choices = c("Extremely liberal",
                     "Somewhat liberal",
                     "Slightly liberal",
                     "Moderate",
                     "Slightly conservative",
                     "Somewhat conservative",
                     "Extremely conservative"),
         selected = "Somewhat liberal",
         width = "450px")

#Fix
selectInput("p1_institution_trust",
         label = "Political institution trust from none to complete:",
         choices = c("No trust at all in political institutions",
                     "Very little trust in political institutions",
                     "Little trust in political institutions",
                     "Nuetral trust in political institutions",
                     "Some trust in political institutions",
                     "A lot of trust in political institutions",
                     "Complete trust in political institutions"),
         selected = "Complete trust in political institutions",
         width = "450px")

selectInput("p1_others_charitable",
         label = "People should be more charitable:",
         choices = c("Strongly disagree",
                     "Disagree",
                     "Somewhat disagree",
                     "Nuetral",
                     "Somewhat agree",
                     "Agree",
                     "Strongly agree"),
         selected = "Strongly agree",
         width = "450px")

# Fix
selectInput("p1_worship_attendance",
         label = "Worship service attendance:",
         choices = c("Not sure",
                     "Rarely attend services",
                     "Attend at least once a month"),
         selected = "Attend at least once a month",
         width = "450px")

selectInput("p1_religion_importance",
         label = "Importance of religion:",
         choices = c("Not important",
                     "Important"),
         selected = "Important",
         width = "450px")

selectInput("p1_religion",
         label = "Religion:",
         choices = c('Catholic',
                     'Protestant',
                     'Christian Orthodox',
                     'Jewish',
                     'Muslim',
                     'Sikh',
                     'Hindu',
                     'Buddhist',
                     'Atheist',
                     'Other (Religion)'),
         selected = 'Protestant',
         width = "450px")

selectInput("p1_charity_importance",
          label = "Charity importance:",
          choices = c("Not at all important",
                      "Very unimportant",
                      "Somewhat unimportant",
                      "Nuetral",
                      "Somewhat important",
                      "Very important",
                      "Essential"),
          selected = "Somewhat unimportant",
          width = "450px")

#Fix
selectInput("p1_trust_in_charity",
            label = "Charity trust:",
            choices = c("No trust at all in charities",
                        "Very little trust in charities",
                        "Little trust in charities",
                        "Nuetral trust in charities",
                        "Some trust in charities",
                        "A lot of trust in charities",
                        "Complete trust in charities"),
            selected = "Complete trust in charities",
            width = "450px")

#Fix
selectInput("p1_donation_frequency",
         label = "Donation frequency:",
         choices = c('Donate more than once a month, less than once a year',
                     'Donate at least once a month'),
         selected = "Donate at least once a month",
         width = "450px")

selectInput("p1_donation_amount",
         label = "Donation amount:",
         choices = c("$1-$49",
                     '$50-$99',
                     '$100-$499',
                     '$500-$999',
                     '$1,000-$4,999',
                     '$5,000-$9,999',
                     '$10,000+'),
         selected = "$100-$499",
         width = "450px")

#Fix
selectInput("p1_volunteer_12",
         label = "Volunteered in last 12 months:",
         choices = c("Haven't volunteered", "Have volunteered"),
         selected = "Have volunteered",
         width = "450px")

#Fix
selectInput("p1_volunteer_frequency",
         label = "Volunteer frequency:",
         choices = c("Haven't volunteered in past 12 months",
                     "Rarely volunteer",
                     "Volunteer more than once a month, less than once a year",
                     "Volunteer at least once a month"),
         selected = "Volunteer at least once a month",
         width = "450px")

# fix
selectInput("p1_personal_activism",
         label = "Personal activism:",
         choices = c('Not personally involved ',
                     'Personally involved'),
         selected = "Personally involved",
         width = "450px")

#Fix
selectInput("p1_family_activism",
         label = "Family activism:",
         choices = c('Family not involved',
                     'Family involved'),
         selected = "Family involved",
         width = "450px")

#Fix
selectInput("p1_religious_member",
         label = "Church membership:",
         choices = c("Don't belong to church membership",
                     'Inactive church member',
                     'Active church member'),
         selected = "Don't belong to church membership",
         width = "450px")

#Fix
selectInput("p1_sport_member",
         label = "Sport or recreational membership:",
         choices = c("Don't belong to sports membership",
                     'Inactive sports member',
                     'Active sports member'),
         selected = "Don't belong to sports membership",
         width = "450px")
#Fix
selectInput("p1_art_member",
         label = "Art, music, or educational membership:",
         choices = c("Don't belong to educational membership",
                     'Inactive educational member',
                     'Active educational member'),
         selected = "Don't belong to educational membership",
         width = "450px")
#Fix
selectInput("p1_labor_member",
         label = "Labor union membership:",
         choices = c("Don't belong to union",
                     'Inactive union member',
                     'Active union member'),
         selected = "Don't belong to union",
         width = "450px")

#Fix
selectInput("p1_political_member",
         label = "Political party membership:",
         choices = c("Don't belong to party",
                     'Inactive party member',
                     'Active party member'),
         selected = "Active party member",
         width = "450px")
# Fix
selectInput("p1_environmental_member",
         label = "Environmental organization membership:",
         choices = c("Don't belong to environmental organization",
                     'Inactive environmental member',
                     'Active environmental member'),
         selected = "Don't belong to environmental organization",
         width = "450px")
# Fix
selectInput("p1_professional_member",
         label = "Professional membership:",
         choices = c("Don't belong to professional membership",
                     'Inactive professional member',
                     'Active professional member'),
         selected = "Don't belong to professional membership",
         width = "450px")
# Fix
selectInput("p1_humanitarian_member",
         label = "Humanitarian organization membership:",
         choices = c("Don't belong to humanitarian organization",
                     'Inactive humanitarian member',
                     'Active humanitarian member'),
         selected = "Active humanitarian member",
         width = "450px")

# Fix
selectInput("p1_consumer_member",
         label = "Consumer organization membership:",
         choices = c("Don't belong to consumer organization",
                     'Inactive consumer member',
                     'Active consumer member'),
         selected = "Don't belong to consumer organization",
         width = "450px")
# Fix
selectInput("p1_other_member",
         label = "Other organization membership:",
         choices = c("Don't belong to other organization",
                     'Inactive other member',
                     'Active other member'),
         selected = "Don't belong to other organization",
         width = "450px")

selectInput("p1_gender",
         label = "Gender:",
         choices = c("Male",
                     "Female",
                     "Transgender",
                     "Prefer not to say",
                     "Other (Gender)"),
         selected = "Male",
         width = "450px")

selectInput("p1_marital_status",
         label = "Marital status:",
         choices = c("Married",
                     "Widowed",
                     "Divorced",
                     "Separated",
                     "Never married"),
         selected = "Married",
         width = "450px")

selectInput("p1_education",
         label = "Education:",
         choices = c("Less than high school",
                     "High school graduate",
                     "Some college",
                     "2 year degree",
                     "4 year degree",
                     "Graduate or professional degree",
                     "Doctorate"),
         selected = "2 year degree",
         width = "450px")

selectInput("p1_income",
         label = "Income:",
         choices = c('Less than median of $61,372',
                     'More than median of $61,372'),
         selected = "More than median of $61,372",
         width = "450px")

selectInput("p1_race",
         label = "Race(s):",
         choices = c('White',
                     'Black or African American',
                     'American Indian or Alaska Native',
                     'Asian',
                     'Native Hawaiian or Pacific Islander',
                     'Other (Race)'),
         multiple = TRUE,
         selected = "White",
         width = "450px")

selectInput("p1_age",
         label = "Age:",
         choices = c('Less than median age of 36',
                     "More than median age of 36"),
         selected = "Less than median age of 36",
         width = "450px")

@@

textInput("p2_id",
          label = "Persona name",
          value = "Persona 2",
          placeholder = "Enter persona name",
          width = "450px")

selectInput("p2_national_news",
         label = "Follow national news:",
         choices = c("Rarely",
                     "Once a week",
                     "At least once a day"),
         selected = "At least once a day",
         width = "450px")

selectInput("p2_international_news",
         label = "Follow international news:",
         choices = c("Never",
                     "Sometimes",
                     "Always"),
         selected = "Always",
         width = "450px")

selectInput("p2_news_medium",
         label = "Medium to follow news:",
         choices = c("TV",
                     "Print",
                     "Online (not social media)",
                     "Social media",
                     "Radio",
                     "Email newsletter",
                     "News app"),
         multiple = TRUE,
         selected = c("TV", "Print", "Social media"),
         width = "450px")

selectInput("p2_follow_gov",
         label = "Follow government & public affairs:",
         choices = c("Not often",
                     "Often"),
         selected = "Often",
         width = "450px")

selectInput("p2_travel_developing",
         label = "Travel to developing country:",
         choices = c("Doesn't travel", "Does travel"),
         selected = "Does travel",
         width = "450px")

selectInput("p2_political_pref",
         label = "Political views from liberal to conservative:",
         choices = c("Extremely liberal",
                     "Somewhat liberal",
                     "Slightly liberal",
                     "Moderate",
                     "Slightly conservative",
                     "Somewhat conservative",
                     "Extremely conservative"),
         selected = "Somewhat liberal",
         width = "450px")

selectInput("p2_institution_trust",
         label = "Political institution trust from none to complete:",
         choices = c("No trust at all in political institutions",
                     "Very little trust in political institutions",
                     "Little trust in political institutions",
                     "Nuetral trust in political institutions",
                     "Some trust in political institutions",
                     "A lot of trust in political institutions",
                     "Complete trust in political institutions"),
         selected = "Complete trust in political institutions",
         width = "450px")

selectInput("p2_others_charitable",
         label = "People should be more charitable:",
         choices = c("Strongly disagree",
                     "Disagree",
                     "Somewhat disagree",
                     "Nuetral",
                     "Somewhat agree",
                     "Agree",
                     "Strongly agree"),
         selected = "Strongly agree",
         width = "450px")

selectInput("p2_worship_attendance",
         label = "Worship service attendance:",
         choices = c("Not sure",
                     "Rarely attend services",
                     "Attend at least once a month"),
         selected = "Attend at least once a month",
         width = "450px")

selectInput("p2_religion_importance",
         label = "Importance of religion:",
         choices = c("Not important",
                     "Important"),
         selected = "Important",
         width = "450px")

selectInput("p2_religion",
         label = "Religion:",
         choices = c('Catholic',
                     'Protestant',
                     'Christian Orthodox',
                     'Jewish',
                     'Muslim',
                     'Sikh',
                     'Hindu',
                     'Buddhist',
                     'Atheist',
                     'Other (Religion)'),
         selected = 'Protestant',
         width = "450px")

selectInput("p2_charity_importance",
          label = "Charity importance:",
          choices = c("Not at all important",
                      "Very unimportant",
                      "Somewhat unimportant",
                      "Nuetral",
                      "Somewhat important",
                      "Very important",
                      "Essential"),
          selected = "Somewhat unimportant",
          width = "450px")

selectInput("p2_trust_in_charity",
            label = "Charity trust:",
            choices = c("No trust at all in charities",
                        "Very little trust in charities",
                        "Little trust in charities",
                        "Nuetral trust in charities",
                        "Some trust in charities",
                        "A lot of trust in charities",
                        "Complete trust in charities"),
            selected = "Complete trust in charities",
            width = "450px")

selectInput("p2_donation_frequency",
         label = "Donation frequency:",
         choices = c('Donate more than once a month, less than once a year',
                     'Donate at least once a month'),
         selected = "Donate at least once a month",
         width = "450px")

selectInput("p2_donation_amount",
         label = "Donation amount:",
         choices = c("$1-$49",
                     '$50-$99',
                     '$100-$499',
                     '$500-$999',
                     '$1,000-$4,999',
                     '$5,000-$9,999',
                     '$10,000+'),
         selected = "$100-$499",
         width = "450px")

selectInput("p2_volunteer_12",
         label = "Volunteered in last 12 months:",
         choices = c("Haven't volunteered", "Have volunteered"),
         selected = "Have volunteered",
         width = "450px")

selectInput("p2_volunteer_frequency",
         label = "Volunteer frequency:",
         choices = c("Haven't volunteered in past 12 months",
                     "Rarely volunteer",
                     "Volunteer more than once a month, less than once a year",
                     "Volunteer at least once a month"),
         selected = "Volunteer at least once a month",
         width = "450px")

selectInput("p2_personal_activism",
         label = "Personal activism:",
         choices = c('Not personally involved ',
                     'Personally involved'),
         selected = "Personally involved",
         width = "450px")

selectInput("p2_family_activism",
         label = "Family activism:",
         choices = c('Family not involved',
                     'Family involved'),
         selected = "Family involved",
         width = "450px")

selectInput("p2_religious_member",
         label = "Church membership:",
         choices = c("Don't belong to church membership",
                     'Inactive church member',
                     'Active church member'),
         selected = "Don't belong to church membership",
         width = "450px")

selectInput("p2_sport_member",
         label = "Sport or recreational membership:",
         choices = c("Don't belong to sports membership",
                     'Inactive sports member',
                     'Active sports member'),
         selected = "Don't belong to sports membership",
         width = "450px")

selectInput("p2_art_member",
         label = "Art, music, or educational membership:",
         choices = c("Don't belong to educational membership",
                     'Inactive educational member',
                     'Active educational member'),
         selected = "Don't belong to educational membership",
         width = "450px")

selectInput("p2_labor_member",
         label = "Labor union membership:",
         choices = c("Don't belong to union",
                     'Inactive union member',
                     'Active union member'),
         selected = "Don't belong to union",
         width = "450px")

selectInput("p2_political_member",
         label = "Political party membership:",
         choices = c("Don't belong to party",
                     'Inactive party member',
                     'Active party member'),
         selected = "Active party member",
         width = "450px")

selectInput("p2_environmental_member",
         label = "Environmental organization membership:",
         choices = c("Don't belong to environmental organization",
                     'Inactive environmental member',
                     'Active environmental member'),
         selected = "Don't belong to environmental organization",
         width = "450px")

selectInput("p2_professional_member",
         label = "Professional membership:",
         choices = c("Don't belong to professional membership",
                     'Inactive professional member',
                     'Active professional member'),
         selected = "Don't belong to professional membership",
         width = "450px")

selectInput("p2_humanitarian_member",
         label = "Humanitarian organization membership:",
         choices = c("Don't belong to humanitarian organization",
                     'Inactive humanitarian member',
                     'Active humanitarian member'),
         selected = "Active humanitarian member",
         width = "450px")

selectInput("p2_consumer_member",
         label = "Consumer organization membership:",
         choices = c("Don't belong to consumer organization",
                     'Inactive consumer member',
                     'Active consumer member'),
         selected = "Don't belong to consumer organization",
         width = "450px")

selectInput("p2_other_member",
         label = "Other organization membership:",
         choices = c("Don't belong to other organization",
                     'Inactive other member',
                     'Active other member'),
         selected = "Don't belong to other organization",
         width = "450px")

selectInput("p2_gender",
         label = "Gender:",
         choices = c("Male",
                     "Female",
                     "Transgender",
                     "Prefer not to say",
                     "Other (Gender)"),
         selected = "Male",
         width = "450px")

selectInput("p2_marital_status",
         label = "Marital status:",
         choices = c("Married",
                     "Widowed",
                     "Divorced",
                     "Separated",
                     "Never married"),
         selected = "Married",
         width = "450px")

selectInput("p2_education",
         label = "Education:",
         choices = c("Less than high school",
                     "High school graduate",
                     "Some college",
                     "2 year degree",
                     "4 year degree",
                     "Graduate or professional degree",
                     "Doctorate"),
         selected = "Some college",
         width = "450px")

selectInput("p2_income",
         label = "Income:",
         choices = c('Less than median of $61,372',
                     'More than median of $61,372'),
         selected = "More than median of $61,372",
         width = "450px")
